\documentclass[format=acmsmall, natbib=false, review=false, anonymous=true, screen=true]{acmart}

% using biblatex
\let\citename\relax
\RequirePackage[abbreviate=true,
 dateabbrev=true,
 natbib=true,
 isbn=false,
 doi=false,
 eprint=false,
 urldate=comp,
 url=false,
 maxbibnames=9,
 backref=false,
 backend=biber,
 style=ACM-Reference-Format,
language=american]{biblatex}

\addbibresource{cscw-comic.bib}
\addbibresource{hari-cscw-comic.bib}
\renewcommand{\bibfont}{\Small}

\usepackage{wrapfig}
\usepackage{booktabs} % For formal tables
\usepackage{cleveref} % for better references
\usepackage{graphicx,subfig,caption}
\usepackage[ruled]{algorithm2e} % For algorithms
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

\usepackage{subfig} % subcaptions
\usepackage{wasysym} % smiley faces

% Metadata Information
% \acmJournal{TWEB}
% \acmVolume{9}
% \acmNumber{4}
% \acmArticle{39}
% \acmYear{2010}
% \acmMonth{3}
% \copyrightyear{2009}
%\acmArticleSeq{9}

% Copyright
%\setcopyright{acmcopyright}
\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{0000001.0000001}

% Paper history
\received{February 2007}
\received[revised]{March 2009}
\received[accepted]{June 2009}


% Document starts
\begin{document}
% Title portion. Note the short title for running heads
\title[Statistical Facts in Comic form]{Are Statistical Facts in Comic Form More Persuasive?}


\author{Ziang Xiao}
\email{zxiao5@illinois.edu, hs1@illinois.edu}
\author{Po-Shiun Ho}
\email{pho11@illinois.edu}
\author{Hari Sundaram}
\email{hs1@illinois.edu}
\affiliation{%
 \institution{University of Illinois}
 \department{Computer Science}
 \city{Urbana}
 \state{IL}
 \postcode{61801}
 \country{USA}}
\author{Xinran Wang}
\email{wangxr1108@126.com}
\affiliation{%
 \institution{Tsinghua University}
 \department{Computer Science}
 \city{Beijing}
 \postcode{100084}
 \country{China}}




\begin{abstract}
 This paper looks at the ability of algorithmically synthesized abstract comic-style messages in communicating statistical facts. In collective action dilemmas such as public health, or for people who track their daily routines, statistical facts are an important factor in enabling individuals to adopt beneficial behaviors. Whether comic representations, despite widespread use in popular culture, offer any tangible benefits over plain text messages in communicating statistical facts is unclear and motivates our study. Drawing on a rich history of the comics (the importance of abstraction) and theories from behavioral economics (information framing) and psychology (social proof), we algorithmically synthesize persuasive messages in an abstract comic form. Through a field experiment, we analyze the effects of key elements in comics on their ability to persuade individuals. Motivated by its use in small sized studies, we use a hierarchical Bayesian model to analyze the results. Our analysis suggests comic representation is significantly more persuasive than text, with a moderate effect size of 0.33. Non-neutral gestures and shading show strong influence, as do negatively framed messages. Further experiments incorporating color suggests that color plays a strong influence.
\end{abstract}


%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
% \begin{CCSXML}
% <ccs2012>
%  <concept>
%   <concept_id>10010520.10010553.10010562</concept_id>
%   <concept_desc>Computer systems organization~Embedded systems</concept_desc>
%   <concept_significance>500</concept_significance>
%  </concept>
%  <concept>
%   <concept_id>10010520.10010575.10010755</concept_id>
%   <concept_desc>Computer systems organization~Redundancy</concept_desc>
%   <concept_significance>300</concept_significance>
%  </concept>
%  <concept>
%   <concept_id>10010520.10010553.10010554</concept_id>
%   <concept_desc>Computer systems organization~Robotics</concept_desc>
%   <concept_significance>100</concept_significance>
%  </concept>
%  <concept>
%   <concept_id>10003033.10003083.10003095</concept_id>
%   <concept_desc>Networks~Network reliability</concept_desc>
%   <concept_significance>100</concept_significance>
%  </concept>
% </ccs2012>
% \end{CCSXML}
%
% \ccsdesc[500]{Computer systems organization~Embedded systems}
% \ccsdesc[300]{Computer systems organization~Redundancy}
% \ccsdesc{Computer systems organization~Robotics}
% \ccsdesc[100]{Networks~Network reliability}

%
% End generated code
%


\keywords{statistical facts, abstract comics, persuasion, information framing, social proof, hierarchical bayesian models}




\maketitle

% The default list of authors is too long for headers.

\input{intro.tex}
\section{Related Work}
\input{relatedwork.tex}
\input{theoreticalframework.tex}
\input{method.tex}
\input{result.tex}
\input{discussion}
\input{conclusion}
\printbibliography
% \bibliographystyle{ACM-Reference-Format}
% \bibliography{sample}
\end{document}
