%!TEX root = cscw2018-comic.tex
In this study, we looked at the ability of comics in persuading people make real decisions. We conducted a field study on Amazon Mechanical Turk and compared the persuasive power between pure text messages and comic messages in persuading people to make charitable giving decisions.

\subsection{Method}
\label{sec:Method}
In this section, we describe our method for evaluating the persuasiveness of comic form messages on real behavior. We will introduce the experiment design and describe our study participants recruiting process.

\subsubsection{Experiment Design}
To compare the persuasiveness of messages in two forms, comic and pure text, we designed a between subject study where participants were randomly assigned to receive the same message either in text, comic, and comic with social norm. The objective of the persuasive message is to persuade participants to donate their perspective bonus rewards (10\% chance of winning \$5 bonus) to a charity.

\paragraph{Organization for Autism Research (OAR)}

To increase the realism of our study, we chose a real charitable organization, the Organization for Autism Research (OAR), that participants will donate to. We chose OAR for the following reasons, 1) The Autism Spectrum Disorder (ASD), a developmental disorder that affects communication and behavior, is a well-known disorder that can affect people in general instead of people in specific area or with specific demographic characters. In other word, ASD is a problem potentially related to every participants in our study, which provides the basic interest for them to support related charitable organization and 2) the Organization for Autism Research is one of the most reputable organization in helping individuals with autism and providing assistance to parents, families, teachers and caregivers. The goal of OAR is clear and reputable so participants won't question the authenticity of our message's motive.

\paragraph{Persuasive Messages}

\paragraph{Study Procedure} Once the participant consents to join the study, they will be asked if he/she is familiar with the Autism Spectrum Disorder (ASD). Then, participant will watch a short-video that promotes OAR's signature fundraising activity "RUN FOR AUTISM". After watch the video, participant will briefly summarize the video and provide their opinion about the effectiveness of the video, which is the task we mentioned in the recruiting message. Then participants will be provided a 10\% chance of winning \$ 5 bonus and asked how much they are willing to donate and support the Organization for Autism Research. The messages were either in pure text or comic form. Before leaving the study, partcipants were asked to fill up some demographic questions.

\subsubsection{Participants}
We published our HITs on Amazon Mechanical Turk titled with ``A short survey about communicating autism campaign ads''. Similar to the Study 1, the price tag is \$8/hr, the workers would get these rewards regardless of their performance, the threshold for participant to join was a 95\% Approval Rate. On the HIT page, and repeated responses will be rejected as instructed, participants would see a link to our experiment site and a text input box for them to enter a six-digit completion code.
